Dipolar~extracellular~potentials generated~by~axonal~projections

### 2017-07-30 doc/manuscript-elife.tex
some tweaks requested by editors. including tweaked bbl file

Acoustic stimuli were digitally generated by a custom-made
\textsc{Matlab} (MathWorks, Natick, MA, USA) script driving a
signal-processing board (RX6, Tucker-Davis Technologies, Alachua, FL,
USA) at a sampling rate of 195.3125~kHz. The sound stimuli were
attenuated using a programmable attenuator (PA5, Tucker-Davis
Technologies). Click stimuli were generated as a single half-wave of a
5~kHz sine tone. Miniature earphones were inserted into the owl's ear
canals and fixed to a headplate. Acoustic stimuli were fed to these
earphones. Stimulus delivery was triggered by National Instruments
equipment (NI USB-6259 and BNC-2090A, National Instruments Inc, Austin,
TX, USA), and stimulus presentation times were recorded along with the
responses. Trigger pulses were configured in \textsc{MatLab} through
Ephus software (Vidrio Technologies LLC, Ashburn, VA, USA). Responses
were averaged over 10 repetitions.

@@

>>>>

Acoustic stimuli were digitally generated by a custom-made
\textsc{Matlab} (MathWorks, Natick, MA, USA; RRID:SCR\_001622) script \citep{GithubRepo} driving a
signal-processing board (RX6, Tucker-Davis Technologies, Alachua, FL,
USA) at a sampling rate of 195.3125~kHz. The sound stimuli were
attenuated using a programmable attenuator (PA5, Tucker-Davis
Technologies). Click stimuli were generated as a single half-wave of a
5~kHz sine tone. Miniature earphones were inserted into the owl's ear
canals and fixed to a headplate. Acoustic stimuli were fed to these
earphones. Stimulus delivery was triggered by National Instruments
equipment (NI USB-6259 and BNC-2090A, National Instruments Inc, Austin,
TX, USA), and stimulus presentation times were recorded along with the
responses. Trigger pulses were configured in \textsc{MatLab} through
Ephus software (Vidrio Technologies LLC, Ashburn, VA, USA). Responses
were averaged over 10 repetitions.

@@

The code for these simulations is available at
\url{https://github.com/phreeza/pyLaminaris} \citep{GithubRepo}.
